Are we living in a depressive society?

### 2024-04-03 outputs/paper/paper.qmd
commit

# Plotting the line graph
ggplot(filtered_data, aes(x = Date, y = Value, group = Indicator, color = Indicator)) +
  geom_line() +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  # Set specific dates as x-axis breaks
  labs(x = "Date",
       y = "Symptom Rates (%)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        plot.margin = unit(c(1, 1, 1, 1), "cm"))

@@

# Plotting the line graph
p <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
  geom_line() +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
  labs(x = "Date", y = "Symptom Rates (%)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none",  # Remove the separate legend
        plot.margin = unit(c(1, 1, 1, 1), "cm"))

>>>>

# Plotting the line graph
ggplot(filtered_data, aes(x = Date, y = Value, group = Indicator, color = Indicator)) +
  geom_line() +
  geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +  # Set specific dates as x-axis breaks
  labs(x = "Date",
       y = "Symptom Rates (%)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.box = "vertical",
        plot.margin = unit(c(1, 1, 1, 1), "cm"))

@@

# Plotting the line graph
p <- ggplot(data, aes(x = Date, y = Value, group = Subgroup, color = Subgroup)) +
  geom_line() +
  geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
  scale_x_date(breaks = specific_dates, date_labels = "%Y-%m-%d") +
  labs(x = "Date", y = "Symptom Rates (%)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none",  # Remove the separate legend
        plot.margin = unit(c(1, 1, 1, 1), "cm"))
